Verifying Demonstrations

### 2017-08-17 SystemModel.tex
Adds Rusuk adversary
Adds WIP on system model

\begin{frame}
\begin{question}
  What is participating in a protest?
  We need a definition.
\end{question}
\mode<presentation>{
\begin{remark}
  \begin{itemize}
    \item This depends on the unique ring/list signature schemes.
    \item I.e.\ when we can no longer guarantee uniqueness.
    \item The one setting up that signature scheme decides.
    \item We don't know how this will be done, nor by whom.
  \end{itemize}
\end{remark}
}
\end{frame}
This sort of depends on the unique ring/list signature scheme that we use.
As long as we can provide linkability between a user's proofs, we can consider 
it the same protest.
When we cannot, it must be a new protest.
So this is supposedly decided by the one setting up the unique ring/list 
signature scheme --- which we do not know yet how it will be done.

\begin{frame}
\begin{remark}
  We provide a lower bound, since there might be participants without phones.
\end{remark}
\begin{remark}
  I.e.\ provided we can prevent Sybil.
\end{remark}
\end{frame}

\begin{frame}
\begin{question}
  What assumptions do we need?
\end{question}

We assume that
\begin{itemize}
  \item Everyone has a smartphone.
  \item Can use ad-hoc networks during the event.
\end{itemize}
\end{frame}

@@

We have two types of adversaries:
\begin{frame}
\begin{itemize}
  \item Eve tries to lower the count.
  \item Eve tries to deanonymize protesters.
\end{itemize}
\end{frame}

>>>>

\subsection{Assumptions}

We assume that every participant has a device similar to a smartphone.
It must be a portable device which can perform cryptographic operations and 
communicate with other devices during the protest, e.g.\ through an ad-hoc 
network.
I.e.\ no connection to the Internet is necessary during the protest.
During the protest these devices are computationally limited by their 
batteries.
Before and after the protest, we assume that the devices have Internet 
connections and are not computationally limited by any battery.

\begin{frame}<presentation>
  \begin{assumption}[During protest]
    \begin{itemize}
      \item Everyone has a smartphone.
      \item Can use ad-hoc networks during the event.
      \item Computations bounded by battery life.
    \end{itemize}
  \end{assumption}

  \pause

  \begin{assumption}[Before and after protest]
    \begin{itemize}
      \item Internet connection available.
      \item Computations not bounded by battery life.
    \end{itemize}
  \end{assumption}
\end{frame}

This means that we essentially provide a lower bound for the participation 
count, since some participants might not have any smartphone.
\begin{frame}
\begin{remark}
  We provide a lower bound, since there might be participants without phones.
\end{remark}
\begin{remark}
  I.e.\ provided we can prevent Sybil.
\end{remark}
\end{frame}

@@

We have three adversaries: Alice herself, Eve and Rusuk.
Alice the protest organizer tries to increase the count.
Eve the totalitarian dictator tries to decrease the count.
Additionally, Eve tries to deanonymize the participants.
Finally, we have Rusuk who is the head of another nation state.
Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
gain, thus supporting either Eve or Alice.
Rusuk will thus also try to either increase or decrease the count.

\begin{frame}<presentation>
  \begin{block}{Alice the activist}
    \begin{itemize}
      \item Alice organizes the protest against Eve's regime.
      \item Alice wants to have a high participation count.
      \item She tries to increase it.
    \end{itemize}
  \end{block}

  \pause

  \begin{block}{Eve the fake-news populist}
    \begin{itemize}
      \item Eve's regime is target of the protest.
      \item She wants to have a low participation count.
      \item She tries to decrease it.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}<presentation>
  \begin{block}{Eve the totalitarian dictator}
    \begin{itemize}
      \item Eve wants to \enquote{convince} activists to support her.
      \item She wants to find all activists.
      \item She tries to identify (deanonymize) participants.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}<presentation>
  \begin{block}{Rusuk the nation state}
    \begin{itemize}
      \item Rusuk benefits from the situation in Evestan.
      \item He wants the outcome to be the most beneficial.
      \item He will try to increase or decrease the participation count.
    \end{itemize}
  \end{block}
\end{frame}

\subsection{System model}

We will define a protest as an event that is uniquely identified by its cause, 
its time and its location.
More specifically, we will use the following definition.

\begin{definition}[Protest]
  A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
  \(id\in \Z_{2^\lambda}\) is an identifier,
  \((t_s, t_e)\in \R^2\) is a time interval,
  \((x, y)\in \R^2\) are the coordinates of the location.
  A \emph{protest} is a set of subprotests.
\end{definition}

\begin{frame}<presentation>
\begin{definition}[Protest]
  \begin{itemize}
    \item A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
    \item \(id\in \Z_{2^\lambda}\) is an identifier,
    \item \((t_s, t_e)\in \R^2\) is a time interval,
    \item \((x, y)\in \R^2\) are the coordinates of the location.
    \item A \emph{protest} is a set of subprotests.
  \end{itemize}
\end{definition}
\end{frame}

The protests described in \cref{WhatIsAProtest} can be captured using this 
definition by splitting them up into subprotests.
Each subprotest will then be captured by our definition and to find the total 
we can just sum up the results.

\begin{frame}
\begin{question}
  With this definition, can we participate in two sub-protests and be counted 
  twice?
\end{question}
\begin{remark}
  Perhaps not if linkability is tied to the cause.
\end{remark}
\end{frame}
\begin{remark}
  This sort of depends on the unique ring/list signature scheme that we use.
  As long as we can provide linkability between a user's proofs, we can consider 
  it the same protest.
  When we cannot, it must be a new protest.
  So this is supposedly decided by the one setting up the unique ring/list 
  signature scheme --- which we do not know yet how it will be done.
\end{remark}
